Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-03-11 paper/rebuttal.txt

We would like to thank all reviewers for their feedback. We will buy an
additional page for the camera ready to enrich the related works section and
improve the text where it was previously cut due to space limitations.
Additional replies:

REVIEW 1

% - novelty
%     - certamente le alternative/sets non sono nuovi; la novita' e' la
%       suddivisione dello spazio di ricerca
%     - cercare roba recente che cita Guo/Bonilla/Viappiani e dimostrare che
%       non esiste nulla di piu' sul punto
%     - diversity in IR esiste [ma non ha lo stesso scopo (non dipende da w)] ma
%       per spazio ci siamo concentrati su related work piu' vicini; si potrebbe
%       comprare una pagina ulteriore nel camera ready per spiegare.
% 
% - set search not analyzed thoroughly
%     - il metodo e' giustificato anche con k=2, che funziona pure bene
%     - k>2 e' utile in base al costo cognitivo; per questo abbiamo messo 2
%       grafici (per query e per iteration); qui si vede il vantaggio di k>2
%     - no messaggio definitivo per via del costo cognitivo e del modello utente;
%       si possono esplorare alternative ma non e' il nostro fuoco; o vederlo
%       come recommendation set (di 5 prendi 1), pero' avvantaggerebbe il nostro
%       metodo
% 
% - *
%     - il fatto che i Bayes siano piu' lenti sono comunque lo stato dell'arte:
%       c'e' un tradeoff tra numero di domande e scalare nel bayesiano; noi
%       invece otteniamo le stesse perf ma scaliamo molto oltre.
%     - gli attributi booleani c'e' un misunderstanding: il problema e' ben
%       piu' complesso. spiegare attributi in dettaglio e quanti bits.

- We agree that using sets of candidates to encourage diversity is not new. Indeed one of the 
  competitors we have is a Bayesian approach for optimal recommendation sets. The
  novelty is in the set-margin formulation adapting the large margin paradigm to this setting.

- Diversity in information retrieval has a different goal, unrelated to
  optimization and learning. We will provide details and further references
  in the additional page. QUESTO LO LEVEREI

- Recently the focus in preference elicitation shifted a bit. Our
  searches in the literature found nothing more appropriate than the
  works we compare to. We'd be grateful for any other relevant
  references.

- The main contribution of the work is that splitting the search space
  in the fashion proposed achieves state-of-the-art performance at a
  fraction of the computational cost. This is certainly true for
  pairwise queries (k=2), where all methods can be compared on a fair
  basis. For k>2, it is difficult to precisely define the cognitive
  load.  That's why we report both per-query and per-iteration 
  results, where the latter show faster convergence for k>2.

- The fact that Bayesian methods are computationally expensive is not
  sufficient to rule them out, as they tend to be more accurate on
  small scale problems. What we show is that we are able to get
  comparable performance on these problems, while scaling much more.

- There is a misunderstanding regarding the complexity of the PC dataset. The
  task is more complex than perceived by the reviewer: a binary encoding of the 
  features would produce 73 boolean attributes, not 7. [RIVEDERE]

### 2016-03-11 paper/rebuttal.txt

- Thanks for the references, we will make sure to include them.
- The margin must be non-negative, as specified in the text above Eq 1; we will
  point it out more clearly.

REVIEW 4

% - BT: forse ci favorisce, ci stiamo solo confrontando con quello che fanno gli
%   altri, preso dai competitors; al contrario, sono i modelli bayesiani che
%   lo sfruttano meglio (o almeno che potrebbero)
% - cognitive load: ha ragione, ma tutti fanno domande a coppie es Guo & Sanner,
%   ci accodiamo. non e' chiaro come formalizzare (chiedere agli psicologi)? e'
%   da investigare. in effetti e' quello che vogliamo fare (trovare query che
%   sono piu' facili per l'utente). ma va oltre lo scopo.
% - scalability: stiamo sempre parlando di interazione con l'utente, quindi siamo
%   lontani dal raggiugnere la complex gestibile da un MILP solver. il PC ad es
%   e' gestibile mentre per l'utente e' complesso (non si va sulle migliaia di
%   var booleane). capire quanti Bools un MILP gestisce (chiedere a Roberto?).
%   la sat del solver sta molto sopra la sat dell'utente.
% - reals: future work di sicuro, infatti l'abbiamo messo li' -- le estensioni
%   sarebbero non-lineari per via di <w,x>, citare ultimo paper sanner. in
%   realta' ongoing su hybrid (alternated o nonlinear).

%- We do not think the BT response model favors our method. First, it was
%  previously used to evaluate the competitors, we merely took it from there.
%  Second, given that Bayesian models are tied to the response model, they are
%  more likely to benefit from the additional constraints that the modelling
%  provides.

- We adopt Bradley Terry (BT) as a response model as it is a common assumption in preference elicitation papers. It is true that constraint 2 induce items that are "different" and will often be associated with a low prob of error according to the BT reponse model.
But we do not think this as giving an unfair advantage to our method; actually it is the Bayesian competitors that exploit BT better, as it is used as an observation model when performing Bayesian updates.

- True, modelling the cognitive load is not easy. We have ongoing work to
  explore this issue further, in collaboration with psychologists. In the
  paper we just followed the common practice of pairwise queries, for
  comparability.
- User resources strongly limit the overall complexity of the MILP problem;
  MILP solvers are well-equipped to solve problems of this magnitude.
- Indeed linearly dependent variables are not very expressive. We are very much
  interested in extending the method to hybrid Boolean/continuous domains, as
  hinted to in the Conclusion. We are currently investigating two directions:
  alternating between optimization of Boolean and continuous variables, and
  leveraging non-linear solvers.
- Thanks for the reference, we'll make sure to include it.

### 2016-03-11 paper/rebuttal.txt

We would like to thank all reviewers for their feedback. We will buy an
additional page for the camera ready to enrich the related works section and
improve the text where it was previously cut due to space limitations.
Additional replies:

REVIEW 1

% - novelty
%     - certamente le alternative/sets non sono nuovi; la novita' e' la
%       suddivisione dello spazio di ricerca
%     - cercare roba recente che cita Guo/Bonilla/Viappiani e dimostrare che
%       non esiste nulla di piu' sul punto
%     - diversity in IR esiste [ma non ha lo stesso scopo (non dipende da w)] ma
%       per spazio ci siamo concentrati su related work piu' vicini; si potrebbe
%       comprare una pagina ulteriore nel camera ready per spiegare.
% 
% - set search not analyzed thoroughly
%     - il metodo e' giustificato anche con k=2, che funziona pure bene
%     - k>2 e' utile in base al costo cognitivo; per questo abbiamo messo 2
%       grafici (per query e per iteration); qui si vede il vantaggio di k>2
%     - no messaggio definitivo per via del costo cognitivo e del modello utente;
%       si possono esplorare alternative ma non e' il nostro fuoco; o vederlo
%       come recommendation set (di 5 prendi 1), pero' avvantaggerebbe il nostro
%       metodo
% 
% - *
%     - il fatto che i Bayes siano piu' lenti sono comunque lo stato dell'arte:
%       c'e' un tradeoff tra numero di domande e scalare nel bayesiano; noi
%       invece otteniamo le stesse perf ma scaliamo molto oltre.
%     - gli attributi booleani c'e' un misunderstanding: il problema e' ben
%       piu' complesso. spiegare attributi in dettaglio e quanti bits.

- First of all, there is a misunderstanding regarding the experiment with the PC dataset. 
The choice space is much larger than perceived by the reviewer: the binary encoding of the 8
features (7 discrete + 1 real) uses 73 boolean attributes. This corresponds to more than 700K feasible configurations.

- While the idea of using sets of candidates to encourage diversity is not new, the
  novelty is in extending the large margin paradigm to sets. We view this as a significant step forward over previous approaches using max-margin maximization and heuristic methods for uncertainty reduction [for example: Gajos 2005].

@@

- Diversity in information retrieval has a different goal, unrelated to
  optimization and learning. We will provide details and further references
  in the additional page. QUESTO LO LEVEREI

- Recently the focus in preference elicitation shifted a bit towards sequential decision making and preference-based reinforcement learning. Our literature search found nothing more appropriate than the works we compare to. We'd be grateful for pointers to other relevant references.

@@

- The main contribution of the work is that splitting the search space
  in the fashion proposed achieves state-of-the-art performance at a
  fraction of the computational cost. This is certainly true for
  pairwise queries (k=2), where all methods can be compared on a fair
  basis. For k>2, it is difficult to precisely define the cognitive
  load.  That's why we report both per-query and per-iteration 
  results, where the latter show faster convergence for k>2.

- The fact that Bayesian methods are computationally expensive is not
  sufficient to rule them out, as they tend to be more accurate on
  small scale problems. What we show is that we are able to get
  comparable performance on these problems, while being able to scale much more.

### 2016-03-11 paper/rebuttal.txt

REVIEW 1

% - novelty
%     - certamente le alternative/sets non sono nuovi; la novita' e' la
%       suddivisione dello spazio di ricerca
%     - cercare roba recente che cita Guo/Bonilla/Viappiani e dimostrare che
%       non esiste nulla di piu' sul punto
%     - diversity in IR esiste [ma non ha lo stesso scopo (non dipende da w)] ma
%       per spazio ci siamo concentrati su related work piu' vicini; si potrebbe
%       comprare una pagina ulteriore nel camera ready per spiegare.
% 
% - set search not analyzed thoroughly
%     - il metodo e' giustificato anche con k=2, che funziona pure bene
%     - k>2 e' utile in base al costo cognitivo; per questo abbiamo messo 2
%       grafici (per query e per iteration); qui si vede il vantaggio di k>2
%     - no messaggio definitivo per via del costo cognitivo e del modello utente;
%       si possono esplorare alternative ma non e' il nostro fuoco; o vederlo
%       come recommendation set (di 5 prendi 1), pero' avvantaggerebbe il nostro
%       metodo
% 
% - *
%     - il fatto che i Bayes siano piu' lenti sono comunque lo stato dell'arte:
%       c'e' un tradeoff tra numero di domande e scalare nel bayesiano; noi
%       invece otteniamo le stesse perf ma scaliamo molto oltre.
%     - gli attributi booleani c'e' un misunderstanding: il problema e' ben
%       piu' complesso. spiegare attributi in dettaglio e quanti bits.

- We agree that using sets of candidates to encourage diversity is not new. Indeed one of the 
  competitors we have is a Bayesian approach for optimal recommendation sets. The
  novelty is in the set-margin formulation adapting the large margin paradigm to this setting.

% - Diversity in information retrieval has a different goal, unrelated to
%  optimization and learning. We will provide details and further references
%  in the additional page. QUESTO LO LEVEREI

@@

- There is a misunderstanding regarding the complexity of the PC dataset. The
  task is more complex than perceived by the reviewer: a binary encoding of the 
  features would produce 73 boolean attributes, not 7. [RIVEDERE]

REVIEW 2

% R2
% 
% - citare UTA in OR -> citare UTA quando introduciamo le slacks
% - ha ragione, rephrase (primo qualita', secondo diversita', tutti e due diversita' dei buoni)
% - non normalizzando i pesi (che e' solo una possibilita'), la L1 e' lo standard
%   per sparsificare
% - explain that the linearization trick is used in Boutilier et al. 2006
% - chiarire che il num bool e sum domini; ma i problemi sono tranquilli perche'
%   i w utenti sono semplici e gli XOR restringono il problema
% - why should gamma be crossvalidated? intuition:
%     - il vincolo 2 diversifica
%     - il gamma vuole che gli oggetti siano di buona qualita' che in PE servono
%       perche' l'utente non si incazzi; non e' ovvio quale deve essere il suo
%       contributo percio' crossvalidiamo
%     - chiarire i bump a cosa sono dovuti (non a gamma); tagliato per spazio
% - fix footnote 4 only applies to k=1 (chiarisco che chiariro')
% - explain why 80% sparsity mimics a user (typically cares about 3 or 4 features)
%     - siamo d'accordo che con 3-4 features non serve la sparsita'; peccato
%       che dobbiamo simularlo su poche features (synth) for sake of comparisons
%       perche su PC gli altri metodi non funzionano
%     - la sparsita' non l'abbiamo introdotta per far vedere che il nostro sys
%       va meglio -- l'idea e' che scaliamo meglio sia in sparso che in denso.
%       ma usarla e' ragionevole per modellare l'utente. non ci costa nulla
%       toglierla, e non cambia la sua utilita'. il confronto non e' sulla
%       sparsita' ma sul fatto che gli altri non scalano)
%       (infatti la scalabilita' e' il nostro cavallo di battaglia)

- Thanks for the reference, it will be integrated.
- Correct, <wi,xi> encourages the quality of the xi's, diversity is given
  by constraint 2. We will rephrase the sentence.
- Fixing the 1-norm is not the only option. In our case, the norm is variable
  and sparsity is encouraged through LASSO. This is a standard approach.
- We will clarify that the linearization trick is taken from elsewhere, and
  refer to the paper by Boutilier.
- User resources strongly limit the overall complexity of the MILP
  problem.  Current MILP solvers can easily deal with problems of this
  magnitude. Concerning extension to real variables, we do not plan to
  binarize them, but rather use appropriate solvers like MIQP
- Gamma controls the importance of candidate item quality for ensuring
  diversity; gamma=0 could be used. Since the correlation is not known
  beforehand, we include gamma in the cross-validation.
- Footnote 4 should only apply to k=1 (as constraint 2 vanishes). Will fix.

- The intuition for the sparse utility is that when many features are
  available, a real user will likely use only few of them. We agree
  with the reviewer that with 3 or 4 features sparsity is not needed,
  but these were the domain sizes our competitors could afford. Please
  note that the scalability of our method does not depend on the
  sparsity assumption, which is rather introduced to account for the
  bounded rationality of users in large decision spaces.

### 2016-03-11 paper/rebuttal.txt

- The fact that Bayesian methods are computationally expensive is not
  sufficient to rule them out, as they tend to be more accurate on
  small scale problems. What we show is that we are able to get
  comparable performance on these problems, while being able to scale much more.

REVIEW 2

% R2
% 
% - citare UTA in OR -> citare UTA quando introduciamo le slacks
% - ha ragione, rephrase (primo qualita', secondo diversita', tutti e due diversita' dei buoni)
% - non normalizzando i pesi (che e' solo una possibilita'), la L1 e' lo standard
%   per sparsificare
% - explain that the linearization trick is used in Boutilier et al. 2006
% - chiarire che il num bool e sum domini; ma i problemi sono tranquilli perche'
%   i w utenti sono semplici e gli XOR restringono il problema
% - why should gamma be crossvalidated? intuition:
%     - il vincolo 2 diversifica
%     - il gamma vuole che gli oggetti siano di buona qualita' che in PE servono
%       perche' l'utente non si incazzi; non e' ovvio quale deve essere il suo
%       contributo percio' crossvalidiamo
%     - chiarire i bump a cosa sono dovuti (non a gamma); tagliato per spazio
% - fix footnote 4 only applies to k=1 (chiarisco che chiariro')
% - explain why 80% sparsity mimics a user (typically cares about 3 or 4 features)
%     - siamo d'accordo che con 3-4 features non serve la sparsita'; peccato
%       che dobbiamo simularlo su poche features (synth) for sake of comparisons
%       perche su PC gli altri metodi non funzionano
%     - la sparsita' non l'abbiamo introdotta per far vedere che il nostro sys
%       va meglio -- l'idea e' che scaliamo meglio sia in sparso che in denso.
%       ma usarla e' ragionevole per modellare l'utente. non ci costa nulla
%       toglierla, e non cambia la sua utilita'. il confronto non e' sulla
%       sparsita' ma sul fatto che gli altri non scalano)
%       (infatti la scalabilita' e' il nostro cavallo di battaglia)

- Thanks for the reference, it will be integrated.
- Correct, <wi,xi> encourages the quality of the xi's, diversity is given
  by constraint 2. We will rephrase the sentence.
- Fixing the 1-norm is not the only option. In our case, the norm is variable
  and sparsity is encouraged through LASSO. This is a standard approach.
- We will clarify that the linearization trick is a classic method in OR, and
  refer to the paper by Boutilier.
- Computational resources limit the adoption of the MILP
  optimization.  Current MILP solvers can easily deal with problems of this
  magnitude. Wrt extension to real variables, we do not plan to
  binarize them, but rather use appropriate solvers like MIQP
- Gamma controls the importance given to the quality of the candidate, since we do want to favour queries with 'good' items in term of utility; in principle gamma=0 could be used.  Since the relation between utility of items in a set and the information value of the query  is not known  beforehand (contrary to the settings investigated by Viappiani&Boutilier), we include gamma in the cross-validation.

- Footnote 4 is only relevant to the case k=1 (as constraint 2 vanishes). Will fix.

- The intuition for the sparse utility is that when a large number of features are
  available, a real user will likely use only few of them. We agree
  with the reviewer that with 3 or 4 features sparsity is not needed,
  but these were the domain sizes suitable for the comparison with Bayesian methods. Please note that the scalability of our method does not depend on the sparsity assumption, which is rather introduced to account for the bounded rationality of users in large decision spaces.

### 2016-04-13 paper/ijcai16.tex
paper: update following the rebuttal.

\usepackage{color}
\newcommand{\andrea}[1]{{\bf \textcolor{blue}{{\fbox{Andrea:} #1}}}}
\newcommand{\stefano}[1]{{\bf \textcolor{green}{{\fbox{Stefano:} #1}}}}
\newcommand{\paolo}[1]{{\bf \textcolor{red}{{\fbox{Paolo:} #1}}}}

@@

\title{Constructive Preference Elicitation by Setwise Max-margin Learning} %with?
\author{ID 2243}

@@

@@

The automated assessment of preferences has received considerable attention,
starting with pioneering works \cite{White1984,JacquetLagreze95} in the OR community.
%In the past decade a number of researchers have considered elicitation of preferences from an artificial intelligence perspective%; within the machine learning field the term preference learning has been catching up.
%While preferences are often assessed using some ad-hoc rules \cite{},
More recently, a number of AI researchers have proposed interactive methods that elicit
preferences in an adaptive way
\cite{chajewska2000,boutilier2002,Wang2003,boutilier2006,guo2010real,viappiani2010optimal},
observing that, by asking informative questions, it is often possible to make near-optimal decisions with only partial preference information.

@@

The second goal requires to jointly maximize the utility of each
$\vx^{i}$ according to its corresponding weight vector $\vw^i$ and its
scoring difference with respect to the other configurations $\vx^j$ in
the set. We achieve this by maximizing the sum of utilities
$\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$ and adding ranking
constraints of the form
$\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq \mu$ for all
$i,j\in[k]$, $i \ne j$.

@@

A straightforward encoding of the above desiderata leads to the
following mixed integer {\em non-linear} optimization problem over the
variables $\mu \in \bbR_{\ge 0}$, $\{ \vw^i \in \bbR^m \}$, $\{ \vx^i \in \{0,1\}^m \}$:
%
{\footnotesize
\begin{align}
    \max
        & \;\; \mu - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \quad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \quad \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge \mu \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \quad \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \veps^{i} \ge 0 \nonumber
%    \\
%        & \;\; \mu \ge 0 \nonumber
\end{align}
}
%
Let us illustrate the above piece by piece. The objective is composed
of four parts: we maximize the shared margin $\mu$ (first part) and
minimize the total sum of the ranking errors $\veps^i$ incurred by
each weight vector $\vw^{i}$ (second part), while at the same time
regularizing the magnitude of the weights (third part) and the quality
of the configurations $\{ \vx^{i} \}$ (last part). The non-negative
hyperparameters $\alpha,\beta,\gamma$ control the influence of the
various components. The weight regularization term copes with the
common scenario in which the user has strong preferences about some
attributes, but is indifferent to most of
them. %~\cite{} \stefano{@Paolo: add refs}.
The $\ell_1$ penalty is frequently used to improve the sparsity of
learned models~\cite{lasso,zhang2008,Hensinger2010}, with consequent
gains in generalization ability and efficiency, as confirmed by our
empirical findings (see
Section~\ref{sec:experiments}). Constraint~(\ref{eq:wyconstr})
enforces the correct ranking of the observed user preferences, while
%constraint
~(\ref{eq:wxconstr}) ensures that the generated
configurations are diverse in terms of the weight vectors they
maximize. Constraints~(\ref{eq:wbounds}) and~(\ref{eq:xbounds}) ensure
that the weights and configurations are feasible, while the last one
guarantees the non-negativity of the slacks.  Since we require
$\vw^\bot \ge (0,\ldots,0)$, Eq.~(\ref{eq:wbounds}) also enforces the
weights to be non-negative.

@@

\paragraph{MILP Formulation.} This initial formulation is problematic to solve,
as Eq.~(\ref{eq:wxconstr}) involves quadratic terms over mixed continuous integer variables. 
Here we show how to reformulate the
problem as a mixed integer linear program (MILP). Our goal is to
replace Eq.~(\ref{eq:wxconstr}) with a set of linear constraints through
a suitable variable transformation.

@@

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^j_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$. Otherwise, if $x^j_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and thus satisfy $p^{i,j}_z = w^i_z
x^j_z$.\footnote{Since $\mu$ is upper-bounded by Eq.~(\ref{eq:wyconstr}), in some
cases the $p^{i,j}_z$ variables do not attain the lower bound. As a
consequence, the MILP reformulation of Eq.~(\ref{eq:wxconstr}) is a (tight)
approximation of the original one. This has no impact on the quality of the
solutions.}

>>>>

\usepackage{color}
\newcommand{\andrea}[1]{{\bf \textcolor{blue}{{\fbox{Andrea:} #1}}}}
\newcommand{\stefano}[1]{{\bf \textcolor{green}{{\fbox{Stefano:} #1}}}}
\newcommand{\paolo}[1]{{\bf \textcolor{red}{{\fbox{Paolo:} #1}}}}
\newcommand{\diff}[1]{{\bf \textcolor{violet}{#1}}}

@@

\title{Constructive Preference Elicitation by Setwise Max-margin Learning}

\author{Stefano Teso \\
University of Trento \\
Trento, Italy \\
teso@disi.unitn.it
\And
Andrea Passerini \\
University of Trento \\
Trento, Italy \\
passerini@disi.unitn.it
\And
Paolo Viappiani \\
Universit\'e Pierre et Marie Curie \\
Paris, France \\
paolo.viappiani@lip6.fr}

@@

\paolo{or Andrea: check whether~\cite{greco2008ordinal} is related and comment
on it, as requested by reviewer 3.}

@@

The automated assessment of preferences has received considerable attention,
starting with pioneering works \cite{White1984,jaquetlsiskos1982} in the OR community.
\paolo{or Andrea, check if it is worth mentioning the review in~\cite{jaquetlsiskos2001},
as highlighted by the fourth reviewer.}
%In the past decade a number of researchers have considered elicitation of preferences from an artificial intelligence perspective%; within the machine learning field the term preference learning has been catching up.
%While preferences are often assessed using some ad-hoc rules \cite{},
More recently, a number of AI researchers have proposed interactive methods that elicit
preferences in an adaptive way
\cite{chajewska2000,boutilier2002,Wang2003,boutilier2006,guo2010real,viappiani2010optimal},
observing that, by asking informative questions, it is often possible to make near-optimal decisions with only partial preference information.

@@

The second goal requires \stefano{reviewer 2, rephrase: to jointly maximize the utility of each
$\vx^{i}$ according to its corresponding weight vector $\vw^i$ and its
scoring difference with respect to the other configurations $\vx^j$ in
the set. We achieve this by maximizing the sum of utilities
$\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$ and} adding ranking
constraints of the form
$\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq \mu$ for all
$i,j\in[k]$, $i \ne j$.

@@

A straightforward encoding of the above desiderata leads to the
following mixed integer {\em non-linear} optimization problem over the
variables $\mu \in \bbR_{\ge 0}$, $\{ \vw^i \in \bbR^m \}$, $\{ \vx^i \in \{0,1\}^m \}$ \stefano{stress non-zero margin requirement}:
%
{\footnotesize
\begin{align}
    \max
        & \;\; \mu - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \quad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge \mu - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \quad \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge \mu \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \quad \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \quad \veps^{i} \ge 0 \nonumber
%    \\
%        & \;\; \mu \ge 0 \nonumber
\end{align}
}
%
Let us illustrate the above piece by piece. The objective is composed
of four parts: we maximize the shared margin $\mu$ (first part) and
minimize the total sum of the ranking errors $\veps^i$ incurred by
each weight vector $\vw^{i}$ (second part), while at the same time
regularizing the magnitude of the weights (third part) and the quality
of the configurations $\{ \vx^{i} \}$ (last part). The non-negative
hyperparameters $\alpha,\beta,\gamma$ control the influence of the
various components. The weight regularization term copes with the
common scenario in which the user has strong preferences about some
attributes, but is indifferent to most of
them. %~\cite{} \stefano{@Paolo: add refs}.
The $\ell_1$ penalty is frequently used to improve the sparsity of
learned models~\cite{lasso,zhang2008,Hensinger2010}, with consequent
gains in generalization ability and efficiency, as confirmed by our
empirical findings (see
Section~\ref{sec:experiments}). Constraint~(\ref{eq:wyconstr})
enforces the correct ranking of the observed user preferences, while
%constraint
~(\ref{eq:wxconstr}) ensures that the generated
configurations are diverse in terms of the weight vectors they
maximize. Constraints~(\ref{eq:wbounds}) and~(\ref{eq:xbounds}) ensure
that the weights and configurations are feasible, while the last one
guarantees the non-negativity of the slacks.  Since we require
$\vw^\bot \ge (0,\ldots,0)$, Eq.~(\ref{eq:wbounds}) also enforces the
weights to be non-negative.

@@

\paragraph{MILP Formulation.} This initial formulation is problematic to solve,
as Eq.~(\ref{eq:wxconstr}) involves quadratic terms over mixed continuous integer variables. 
Here we show how to reformulate the
problem as a mixed integer linear program (MILP). Our goal is to
replace Eq.~(\ref{eq:wxconstr}) with a set of linear constraints through
a suitable variable transformation; \stefano{this technique has already been
used in OR~[Boutilier et al., 2006]}.

@@

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^j_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$. Otherwise, if $x^j_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and thus satisfy $p^{i,j}_z = w^i_z
x^j_z$.\footnote{\stefano{This is only relevant for $k=1$.} Since $\mu$ is upper-bounded by Eq.~(\ref{eq:wyconstr}), in some
cases the $p^{i,j}_z$ variables do not attain the lower bound. As a
consequence, the MILP reformulation of Eq.~(\ref{eq:wxconstr}) is a (tight)
approximation of the original one. This has no impact on the quality of the
solutions.}
